An examination of the high-order dynamic interactions underlying multi-dimensional timeseries data

### 2019-04-06 paper/boneyard.tex
updated abstract

>>>>

  Most complex systems reflect dynamic interactions between myriad
  evolving components (e.g., interacting molecules, interacting brain
  systems, interacting individuals within a social network or
  ecological system, coordinated components within a mechanical or
  digital device, etc.).  Despite that these interactions are central
  to the full system's behavior (e.g., removing a component from the
  full system can change the entire system's behavior), dynamic
  interactions cannot typically be directly measured.  Rather, the
  interactions must be inferred through their hypothesized role in
  guiding the dynamics of system components.  Here we use a
  model-based approach to inferring dynamic interactions from
  timeseries data.  In addition to examining first-order interactions
  (e.g., between pairs of components) we also examine higher-order
  interactions (e.g., that characterize mirrored structure in the
  patterns of interaction dynamics displayed by different subsets of
  components).  We apply our approach to two datasets.  First, we use
  a synthetic dataset, for which the underlying dynamic interactions
  are known, to show that our model recovers those ground-truth
  dynamic interactions.  We also apply our model to a neuroimaging
  dataset and show that the high-order dynamic interactions exhibited
  by brain data vary meaningfully as a function of the cognitive
  ``richness'' of the stimulus people are experiencing.
